\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 appendix.tex
Language changes in the appendix

Our plan is to demo the basic usage of J-ReCoVer over two examples. The first example is a reducer that is not commutative, and J-ReCoVer will report a counterexample. Based on this counterexample, we will fix the reducer to get the 2nd example, and let J-ReCoVer to check it again. Now J-ReCoVer will report the reducer is commutative. Below we give a more detailed description of the functionalities of J-ReCoVer.

@@

Figure~\ref{fig:main_screen} shows the main screen of J-ReCoVer. The alignment of user interface elements are as follows:

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.9\linewidth]{screenshots/main_screen}
% \vspace{-5pt}
\caption{Main Screen of J-ReCoVer}
\label{fig:main_screen}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{itemize}
\item
Top Menu:
\begin{itemize}
\item
\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
\item
\emph{``Benchmark''} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows. Select the filename or "try it" button will select the example and go back to the main screen.
\end{itemize}
\item
Right Menu:
\begin{itemize}
\item
\emph{``Benchmark List''} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
\item
\emph{``Results''} shows the last analysis result.
\end{itemize}
\item
Upper-Right Menu:
\begin{itemize}
\item
\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
\item
\emph{``Run''} starts the analysis of the selected example.
\end{itemize}
\item
Upper-Left Menu: See~\ref{appendix:3}.
\end{itemize}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/benchmark_list}
% \vspace{-5pt}
\caption{Benchmark list from top menu (part)}
\label{fig:benchmark_list}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/benchmark_list_right}
% \vspace{-5pt}
\caption{Benchmark list from right menu (part)}
\label{fig:benchmark_list_right}
% \vspace{-15pt}
\end{center}
\end{figure}

\subsection{Run analysis of selected benchmark example}
\label{appendix:2}

To run analysis, you can choose an example from benchmark using either the top menu or the right menu, then click the "Run" button of the upper-right menu to start the commutativity analysis of the selected example. The pull-down menu "Types" of the upper-right menu provides selectable types for input \texttt{(T1,T2)} and output \texttt{(T3,T4)} key-value pairs. Fig.~\ref{fig:type_select_menu} shows the pull-down menu and Fig.~\ref{fig:selectable_types} shows part of the selectable types in J-ReCoVer. If one selects an example from the benchmark, the types will be automatically selected to match the example. The selection will be needed if the user wants to write a reduce function from sketch for analysis (see~\ref{appendix:3}).

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/type_select_menu}
% \vspace{-5pt}
\caption{Type select menu}
\label{fig:type_select_menu}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/selectable_types}
% \vspace{-5pt}
\caption{Selectable types (part)}
\label{fig:selectable_types}
% \vspace{-15pt}
\end{center}
\end{figure}

After J-ReCoVer finishes the analysis, the \emph{"Result:"} tab of the right menu will show the result of the analysis, which can be found in Figure~\ref{fig:analysis_result}. Figure~\ref{fig:analysis_result_text} shows the complete analysis report of the benchmark \texttt{dis.java} in Figure~\ref{fig:main_screen}.

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/analysis_result}
% \vspace{-5pt}
\caption{The analysis result}
\label{fig:analysis_result}
% \vspace{-15pt}
\end{center}
\end{figure}

@@

Key: [s]
Val: [0.0]
--------
Input1: v [-3, -2, 3, 3, -3]
Input2: v [3, -2, -3, -3, 3]
\end{Verbatim}
\end{mdframed}
\caption{The analysis result of \texttt{dis.java}}
\label{fig:analysis_result_text}
\end{center}
\end{figure}

In a commutativity analysis, J-ReCoVer first tries to compile the example then perform commutativity analysis. If the analysis can not conclude that the example is commutative, J-ReCoVer then runs 500 randomly generated test cases to try to find a counterexample. If the test cases all pass, then the result will be "unknown".

\subsection{Run analysis of an example from sketch}
\label{appendix:3}

Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user defined reducer function.
The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are

@@

, and

@@

In this case, one would have to manually fill the types T1 to T4 and the function body, then selects the types from the pull-down menu, as shown in Figure~\ref{fig:type_select_menu} and Figure~\ref{fig:selectable_types}.

For more details, all selectable types are:

\begin{itemize}
\item Long
\item BooleanWritable
\item BytesWritable
\item Text
\item Double
\item DoubleWritable
\item Float
\item FloatWritable
\end{itemize}

>>>>

Our plan is to demonstrate the basic usage of J-ReCoVer on two examples. The
first example is a reducer that is not commutative, and J-ReCoVer will report a
counterexample. Based on this counterexample, we will fix the reducer to get the
second example, and let J-ReCoVer to check it again. Now, J-ReCoVer will report
that the reducer is commutative. Below, we give a more detailed description of
the functionalities of J-ReCoVer.

@@

Figure~\ref{fig:main_screen} shows the main screen of J-ReCoVer.

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.9\linewidth]{screenshots/main_screen_marked}
% \vspace{-5pt}
\caption{The main screen of J-ReCoVer.}
\label{fig:main_screen}
% \vspace{-15pt}
\end{center}
\end{figure}

The alignment of the user interface elements in the main screen is as follows:
\begin{itemize}
\item
Top Menu:
\begin{itemize}
\item
\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository
does also contain the source code of our benchmarks.
\item
\emph{``Benchmark''} leads to the list of benchmarks we collected with their
results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows. Select
a file name or use the ``try it'' button to select an example and go back to the main screen.
\end{itemize}
\item
Right Menu:
\begin{itemize}
\item
\emph{``Benchmark List''} provides a quick selection of examples in the
benchmark (Fig.~\ref{fig:benchmark_list_right}).
\item
\emph{``Results''} shows the last analysis result.
\end{itemize}
\item
Upper-Right Menu:
\begin{itemize}
\item
\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in
Appendix~\ref{appendix:3}.
\item
\emph{``Run''} starts the analysis of the selected example.
\end{itemize}
\item
Upper-Left Menu: See Appendix~\ref{appendix:3}.
\item
Coding Space.
\end{itemize}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/benchmark_list}
% \vspace{-5pt}
\caption{A benchmark list from the top menu (a part).}
\label{fig:benchmark_list}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/benchmark_list_right}
% \vspace{-5pt}
\caption{A benchmark list from the right menu (a part).}
\label{fig:benchmark_list_right}
% \vspace{-15pt}
\end{center}
\end{figure}

\subsection{Run Analysis of a Selected Benchmark Example}
\label{appendix:2}

To run the analysis, one can choose an example from the benchmark using either
the top menu or the right menu and then click the ``Run'' button of the
upper-right menu to start the commutativity analysis of the selected example.
The pull-down menu ``Types'' of the upper-right menu provides selectable types
for input \texttt{(T1,T2)} and output \texttt{(T3,T4)} key-value pairs.
Fig.~\ref{fig:type_select_menu} shows the pull-down menu and
Fig.~\ref{fig:selectable_types} shows a part of the selectable types in
J-ReCoVer.  If one selects an example from the benchmark, the types will be
automatically selected to match the example. The selection will be needed if the
user wants to write a reduce function for analysis  from scratch (see
Appendix~\ref{appendix:3}).

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/type_select_menu}
% \vspace{-5pt}
\caption{The type selection menu.}
\label{fig:type_select_menu}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/selectable_types}
% \vspace{-5pt}
\caption{Selectable types (a part).}
\label{fig:selectable_types}
% \vspace{-15pt}
\end{center}
\end{figure}

After J-ReCoVer finishes the analysis, the \emph{``Result:''} tab of the right
menu will show the result of the analysis, which can be found in
Figure~\ref{fig:analysis_result}. Figure~\ref{fig:analysis_result_text} shows
the complete analysis report of the benchmark \texttt{dis.java} in
Figure~\ref{fig:main_screen}.

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.8\linewidth]{screenshots/analysis_result}
% \vspace{-5pt}
\caption{The analysis result.}
\label{fig:analysis_result}
% \vspace{-15pt}
\end{center}
\end{figure}

@@

Key: [s]
Val: [0.0]
--------
Input1: v [-3, -2, 3, 3, -3]
Input2: v [3, -2, -3, -3, 3]
\end{Verbatim}
\end{mdframed}
\caption{The analysis result of \texttt{dis.java}.}
\label{fig:analysis_result_text}
\end{center}
\end{figure}

When an analysis is started, J-ReCoVer first tries to compile the chosen example
and then performs its commutativity analysis. If the analysis cannot conclude
that the example is commutative, J-ReCoVer then runs 500 randomly generated test
cases to try to find a counterexample. If the test cases all pass, then the
result will be ``unknown''.

\clearpage
\subsection{Run Analysis of a User-defined Reducer Function}
\label{appendix:3}

Besides examples from the benchmark, J-ReCoVer also provides an interactive way
for analysing a user-defined reducer function.  One can directly edit the code
of a selected example in the coding space for further analysis, or write a
reducer function from scratch. The upper-left menu (below the top menu)
provides blank templates for two versions of Hadoop. The templates are shown
below:

@@

@@

In this case, one would have to manually fill the types T1 to T4 and the
function body, and then select the types from the pull-down menu as shown in
Figure~\ref{fig:type_select_menu} and Figure~\ref{fig:selectable_types}. All
selectable types are:

\begin{itemize}
\item Long,
\item BooleanWritable,
\item BytesWritable,
\item Text,
\item Double,
\item DoubleWritable,
\item Float,
\item FloatWritable.
\end{itemize}
